Integrated farming and global warming mitigation in Brazil

### 2022-08-12 manuscript/manuscript.qmd
Fix typo.
Improve objectives section.

library(DiagrammeR)
```

@@

1. Develop an overview about the ICLF experiments characteristics being conducted in Brazil;

    1.1. What is the productivity of each component of ICLF systems of different characteristics?

    1.2. What are the effects of ICLF systems over soils characteristcs?

    1.3. What are the management characteristics of ICLF systems?

    1.4. WHat is the economical revenue of ICLF systems?

    1.5. What is the pottential expansion of ICLF systems in Brazil?

2. Estimate the potential of ICLF systems to remove carbon from the atmosphere by 2030 and 2050;

@@

    2.3. What is the pottential of the expansion of ICLF systems in the emissions reduction pledges made by Brazil?

3.  Evaluate the feasibility of the implementation of ICLF as a mean to reduce emissions, in relation to different perspectives of solutions to avoid climatic catastrophe;

    3.1. Does the expansionof ICLF systems taking into account equity and possible social impacts, as a public policy?

>>>>

library(DiagrammeR)

@@

1. Identify ICLF systems characteristics and dynamics in Brazil;

    1.1. What are the management characteristics of ICLF systems?

    1.2. What are the compositions of each component of ICLF systems?

    1.3. What is the productivity of each component of ICLF systems?

    1.4 What are the effects of ICLF system over soil properties?

    1.5. What is the economical revenue of ICLF systems?

    1.6. What is the potential expansion of ICLF systems in Brazil?

2. Estimate the potential of ICLF systems to provide benefits, in the context of climate change;

@@

    2.3. What is the pottential of the expansion of ICLF systems over the emissions reduction pledges made by Brazil?

3.  Evaluate the implementation of ICLF as a mean to curb and mitigate climate change, in relation to different perspectives of solutions to avoid climatic catastrophe;

    3.1. Does the expansion of ICLF systems taking into account equity and possible social impacts, as a public policy?
